### 2014-01-15 src/paper.Rnw
update

@@

\begin{figure*}[t]
<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4))
hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4))
hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4))
hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
@
\caption{Plots}
\label{fig:caddrm}
\end{figure*}

>>>>

Offutt\cite{offutt1996anexperimental} following the previous paper\cite{offutt1993experimental} compares the effectiveness of selecting different operators. He divides the total operators into operand, operation, and statement categories, with es-selective avoiding operands, rs-selective avoiding operations, and re-selective avoiding statements, and e-selective only operations. He finds that using only operation based mutation operators (numbering 5) is sufficient for close approximation of full mutation score. He suggests that the reason they are effective is that most statements contain operators. He further posits that another reason is the amount of semantic change accomplished by an operator, and perhaps the most interesting ones are those that produce the smallest semantic difference.
% Replacement of Operand , Statement modification, Expression Modification: modify operators, ES-selective : not using operand, RS-Selective: not using expression, RE-Selective: not uinsg statement, E-selective : only expression..

Unch\cite{untch2009onreduced} suggested using a single mutagen statement deletion. He compares the statement deletion with other selective mutagen sets, and finds statement deletion operator to provide the best prediction of original mutation score ($R^2 = 0.97$)

@@

\begin{figure*}[t]
<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(total) mutation score')
hist(log(10,m$pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))
@
\caption{Plots}
\label{fig:caddrm}
\end{figure*}
